Informing policy via dynamic models: Cholera in Haiti

### 2023-08-22 ms-plos.Rnw
removed parallel back-end from haitipkg

# Get the number of cores. The high performance computing cluster that we
# used has 36 cores.
cores <-  as.numeric(Sys.getenv('SLURM_NTASKS_PER_NODE', unset=NA))
if(is.na(cores)) cores <- detectCores()
registerDoParallel(cores)

>>>>

# Get the number of cores. The high performance computing cluster that we
# used has 36 cores.
cores <-  as.numeric(Sys.getenv('SLURM_NTASKS_PER_NODE', unset=NA))
if(is.na(cores)) cores <- detectCores()

# Register parallel back-end. This code below creates a fork cluster, so we are assuming
# that the code is run on a mac or linux machine; this doesn't matter if you
# plan on simply loading the results, but if you would like to redo the expensive
# calculations (e.g., test minor changes to the code), you need to make sure you
# register the correct parallel back-end.
registerDoParallel(cores)
